RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
prefer to use "document" instead of "file", as NeXML data can be obtained from a handle that reads from a remote location, i.e. the data never reside as a file in the system
although this is denormalized into just trees, data and metadata, NeXML documents have four components, not three.
typo fix, re-flow of paragraph

A NeXML file can be thought of as having three components: (1) phylogeny
data (2) character-trait data, and (3) metadata. `RNeXML` seeks to
provide a seemless way to convert these to and from their corresponding
R object representations, such as `ape::phylo` phylogenies, character
matrices (`data.frames`) and metadata lists (or for advanced users,
`XMLInternalDocument` and `rrdf` triplestores). Metadata can provide
information about the study in which the phylogeny was generated or
applied (such as authors, citations to publications, timestamps, and even
descriptions of methods), but can also be used to annotate individual
data components.  We illustrate how metadata annotations can be added to
the operational taxonomic units of the phylogeny and can be used to extend
the data representation to new uses such as stochastic character maps.

@@

The resulting `nex` object is an R object representation of the NeXML.  
This is a native R object for representing phylogenetic trees (as well as 
character traits, and metadata), analgous to the `phylo` object from the 
popular `ape` R package `r citep(citation("ape"))`.

>>>>

A NeXML document can be thought of as having multiple components: (1) phylogeny
data (2) character-trait data, (3) operational taxonomic units, and (4) metadata. 
`RNeXML` seeks to provide a seemless way to convert these to and from their 
corresponding R object representations, such as `ape::phylo` phylogenies, character
matrices (`data.frames`) and metadata lists (or for advanced users,
`XMLInternalDocument` and `rrdf` triplestores). Metadata can provide
information about the study in which the phylogeny was generated or
applied (such as authors, citations to publications, timestamps, and even
descriptions of methods), but can also be used to annotate individual
data components.  We illustrate how metadata annotations can be added to
the operational taxonomic units of the phylogeny and can be used to extend
the data representation to new uses such as stochastic character maps.

@@

The resulting `nex` object is an R object representation of the NeXML. This is 
a native R object for representing phylogenetic trees (as well as 
character traits, and metadata), analogous to the `phylo` object from the 
popular `ape` R package `r citep(citation("ape"))`.
